Capstone Movielens Report

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Summary): print_log2, print_log3, print_log4.

Prints a string formed from the template passed in the [msg_template](#func.print_log2.args.msg_template) argument using the format values specified by the [arg1](#func.print_log2.args.arg1) and [arg2](#func.print_log2.args.arg2) arguments.

@@

Prints a string formed from the template passed in the [msg_template](#func.print_log3.args.msg_template) argument using the format values specified by the [arg1](#func.print_log3.args.arg1), [arg2](#func.print_log3.args.arg2), and [arg3](#func.print_log3.args.arg3) arguments.

@@

Prints a string formed from the template passed in the [msg_template](#func.print_log4.args.msg_template) argument using the format values specified by the [arg1](#func.print_log4.args.arg1), [arg2](#func.print_log4.args.arg2), [arg3](#func.print_log4.args.arg3), and [arg4](#func.print_log4.args.arg4) arguments.

>>>>

Prints a log created from the template passed in the [msg_template](#func.print_log2.args.msg_template) argument, using the values specified by the [arg1](#func.print_log2.args.arg1) and [arg2](#func.print_log2.args.arg2) arguments to replace all the occurrences of the placeholders `%1` and `%2`, respectively, found in the template.

@@

Prints a log created from the template passed in the [msg_template](#func.print_log3.args.msg_template) argument, using the values specified by the [arg1](#func.print_log3.args.arg1), [arg2](#func.print_log3.args.arg2), and [arg3](#func.print_log3.args.arg3) arguments to replace all the occurrences of the placeholders `%1`, `%2`, and `%3`, respectively, found in the template.

@@

Prints a log created from the template passed in the [msg_template](#func.print_log4.args.msg_template) argument, using the values specified by the [arg1](#func.print_log4.args.arg1), [arg2](#func.print_log4.args.arg2), [arg3](#func.print_log4.args.arg3), and [arg4](#func.print_log4.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
